---
title: "STA304 Marriage License Statistics in 2024"
author: 
  - Wen Han Zhao
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Investigate the numbers of Marriage licensed in Toronto in year 2024"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```


# Introduction

We have simulated a data of Marriage licensed throughout 2024 and imported from Toronto Dataset. 

@Torontodata

We have used @ChatGPT to generate some codes for us and @Rohan for insight on this project. 



# Graph and Data 

Some of our data is from Toronto Dataset. 

```{r}

data |> 
  ggplot(aes(x = date,
             y = marriage_licenses)) +
  geom_point() +
  labs(
    title = "Distribution of Toronto Marriages in 2024", 
    x = "Date", 
    y = "Marriage Licenses "
  )
```



# Results

The above graph shows a scatterplot of marriages in 2024 in Toronto. It varies by months. 


# Discussion

## Weaknesses and next steps

Weakness is that the dataset might be too small. 

\newpage

\appendix

# Appendix {-}


# Additional data details




# References


